Interpretable Machine Learning

### 2017-11-23 talk.Rmd
create narrative

@@

##
![](images/machine-learning-xkcd.png)

@@

## Predicting house prices
TODO: Add example dataset

## PDP

## ICE

## LIME

## The big picture

## Book

>>>>

##

![](images/wow.jpg)

# Let's predict data scientist salaries

@@

Machine learning is a method for teaching computers to make and improve predictions or behaviours based on data.

![](images/magic.jpg)

## Step 1: Find some data
Kaggle conducted an industry-wide survey of data scientists. 
Questions asked:

- Demographic
- Salary
- Are you currently enrolled as a student at a degree granting school?	
- How adequately do you feel your title describes what you do (or what you did if retired)?	
- How long have you been learning data science?

TODO: Add only relevant questions here for analysis

```{r load-data, warning=FALSE, include=FALSE}
library('mlr')
library('ggplot2')
source('code/prepare-kaggle-data.R')
```

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
n = getTaskSize(task)
lrn = makeLearner('regr.randomForest', importance=TRUE)
mod = train(lrn, task, subset = seq(1, n, 2))
pred = predict(mod, task = task, subset = seq(2, n, 2))
## TODO: Find better variables https://www.kaggle.com/kaggle/kaggle-survey-2017/data
```
## Step 3: Profit. We are done! {.center}

```{r, echo=FALSE}
knitr::include_graphics("images/done-here.gif")
```

##

![](images/Hide-the-pain-harold-phone.jpg)

## "There is a problem with the model!"
![](images/age.jpeg)

## Individual Conditional Expectation

```{r}
ice = generatePartialDependenceData(mod, task, features =c('Age'), 
                                     individual = TRUE)
plotPartialDependence(ice) + scale_y_continuous(limits=c(0, NA))
```

## ICE, centered

```{r}
ice.centered = generatePartialDependenceData(mod, task, 
                features =c('Age'), individual = TRUE, center = list(Age=20))
plotPartialDependence(ice.centered)
```

## Partial dependence plots
```{r}
pdp = generatePartialDependenceData(mod, task, features =c('Age'))
plotPartialDependence(pdp) + scale_y_continuous(limits=c(0, NA))
```

## "We want to understand the model better!"

## Permutation feature importance

```{r, warning=FALSE}
feat.imp = getFeatureImportance(mod, type=1)
knitr::kable(t(feat.imp$res))
```

## Gender?

```{r}
pdp = generatePartialDependenceData(mod, task, features =c('GenderSelect'))
knitr::kable(pdp$data)
```

##

![](images/hidden-pain-bias.jpg)

##

TODO: Add zoomed in version of Hidden Pain Harolds face

## "We want to understand each decision!"

Based on Game theory. 
TODO: Add visualisation

TODO: Calculate shapley value for one instance.

@@

## Book
Interested in learning more!

Read my book: https://christophm.github.io/xai-book/
